intRo

### 2015-08-12 jsm-2015/eric/index.Rmd
Blank space
Some small changes

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare"
date: "January 12, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP` is powerful, but too big
      - Licenses and inconsistent UI
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software

@@

# Live Demo

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Eric Hare & Andee Kaplan"
date: "August 12, 2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

@@

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP` is powerful, but lots of functionality for intro stats
      - Software licensing issues
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software

@@

# Live Demo
Feel free to try intRo yourself at

http://www.intro-stats.com
